### 2020-08-11 paper/sex_selection_spacing-ver4.tex
Rewrite Abstract to focus on main questions

% Demography abstract
\noindent 
Using four rounds of India's National Family and Health Surveys and a
competing-risk hazard model, I show that Hindu women's birth intervals
increased over the last four decades, more so the higher the parity and
the more educated the woman. 
Women most likely to use sex selection---well-educated with no sons---had the most 
substantial lengthening of birth intervals and the most biased sex ratios. 
However, the likelihood of very short spacing did not change substantially. 
As a result of the longer spacing, fertility rates significantly
overestimated how fast cohort fertility fell. 
Although cohort fertility
and the fertility rate have started to converge, the cohort fertility is
still substantially higher than the fertility rate. 
Furthermore, cohort fertility is still at or above replacement level for all but the
best-educated urban women. 
Finally, infant mortality risk has declined substantially over time for all groups, but 
fastest for the lower education groups, who are now close to the level of women with the most
education. 
Short birth spacing is still associated with higher mortality, although substantially less 
so for the best-educated women. 
There is no evidence that the increasing use of sex selection is associated with
higher infant mortality risk.

@@

% What has happened to spacing and why
The most substantial lengthening of birth intervals came from the best-educated women
because of their substantial use of sex selection combined with falling fertility.
As the sex ratio increased to almost 80 percent boys, the expected median birth interval 
for a woman with twelve or more years of education who has two girls increased by almost 
15 months, and the 75th percentile interval by 21 months.
Most of that increase came right after the introduction of sex selection in India.

>>>>

% Demography abstract
\noindent 
In India, the most substantial lengthening in Hindu women's birth intervals over the last 
four decades occurred for the women most likely to use sex-selective abortions. 
For well-educated women with two girls, the median birth interval to the third child 
increased by nearly 15 months---and the 75th percentile interval by 21 months---as the 
sex ratio approached 80 percent boys. 
Because of the rapid lengthening in spacing, standard fertility rates significantly 
overestimated how fast cohort fertility fell. 
Despite convergence, cohort fertility is still ten to twenty percent higher than the 
fertility rate, and above replacement level for all but the best-educated urban women. 
With the lengthening from sex selection, some women show a reversal of the traditional 
spacing pattern; instead of the shortest birth interval in the absence of sons, they now 
have the longest. 
Finally, infant mortality has declined over time for all groups, but the decline was the 
fastest for the less educated. 
Short birth spacing is still associated with higher mortality, although considerably less 
so for the best-educated women. 
There is no evidence that the increasing use of sex selection is associated with higher 
infant mortality. 
Neither does it appear that the use of sex selection is declining.

% I show that, in India, the most substantial increases in Hindu women's
% birth interval over the last four decades came from the increasing use
% of sex-selective abortions. The women most likely to use sex
% selection---well-educated with no sons---had the most substantial
% lengthening of birth intervals and the most biased sex ratios.

@@

% What has happened to spacing and why
The most substantial lengthening of birth intervals came from the best-educated women
because of their substantial use of sex selection combined with falling fertility.
As the sex ratio increased to almost 80 percent boys, the expected median birth interval 
for a woman with twelve or more years of education who has two girls increased by almost 
15 months, and the 75th percentile interval by 21 months.
Most of the increase in the long intervals came right after the introduction of sex 
selection in India.
